Two-Dimensional Hydrodynamics of a Janus Particle Vesicle

### 2022-02-16 doc/Supplementary.tex
final updates

\noindent 
Szu-Pei Fu$^{1,*},$ 
Bryan Quaife$^{2},$ 
Rolf J. Ryham$^{1},$ 
Y.-N. Young$^{3},$
\\

@@

\noindent
{\bf Movie S6. Single Vesicle Suspended in an Extensional Flow} 
There are two relaxed JP vesicles suspended in a shear flow.The centroid of the left JP vesicle is 0.25 nm above the $x$-axis and the right JP vesicle is 0.25 nm below the $x$-axis. The colored field from dark blue to dark red shows the magnitude of hydrophobic attraction activity and the range is from 0 to 1. All white dots in the domain represent the tracers in fluid that move with respect to calculated fluid motion.
This movies includes a total 6000 time steps where the time step is $\Delta t=0.2$.\\

%%%\end{document}

>>>>

\noindent 
Szu-Pei Fu$^{1,*},$ 
Bryan Quaife$^{2},$ 
Rolf Ryham$^{1},$ 
Y.-N. Young$^{3},$
\\

@@

\noindent
{\bf Movie S6. Two Vesicles Suspended in an Extensional Flow} 
There are two relaxed JP vesicles suspended in an extensional flow. The centroid of the left JP vesicle is 0.25 nm above the $x$-axis and the right JP vesicle is 0.25 nm below the $x$-axis. The colored field from dark blue to dark red shows the magnitude of hydrophobic attraction activity and the range is from 0 to 1. All white dots in the domain represent the tracers in fluid that move with respect to calculated fluid motion.
This movies includes a total 6000 time steps where the time step is $\Delta t=0.2$.
%%%\end{document}
